Stimuli Selection 2

### 2024-10-02 study2/stimuli_selection2/selection2.qmd
study 2 qmd small changes

### Select based on norms
```{r}
men <- napsero2 |>
  filter( Category != "Non-erotic") |>
  group_by(Category) |>
  slice_max(Hetero_Men_Arousal, n=8, with_ties = FALSE) |>
  pull(ID) |> 
  c(
    napsero2 |>
      filter( Category != "Non-erotic") |>
      group_by(Category) |>
      slice_min(Hetero_Men_Arousal, n=2, with_ties = FALSE) |>
      pull(ID))

homo_men <- napsero2 |>
  filter( Category != "Non-erotic") |>
  group_by(Category) |>
  slice_max(Homo_Men_Arousal, n=8, with_ties = FALSE) |>
  pull(ID) |> 
  c(
    napsero2 |>
      filter( Category != "Non-erotic") |>
      group_by(Category) |>
      slice_min(Homo_Men_Arousal, n=2, with_ties = FALSE) |>
      pull(ID))

women <- napsero2 |>
  filter(Category != "Non-erotic", !ID %in% men) |>
  group_by(Category) |>
  slice_max(Hetero_Women_Arousal, n=8, with_ties = FALSE) |>
  pull(ID) |> 
  c(
    napsero2 |>
      filter(Category != "Non-erotic", !ID %in% men) |>
      group_by(Category) |>
      slice_min(Hetero_Women_Arousal, n=2, with_ties = FALSE) |>
      pull(ID)
  )

homo_women <- napsero2 |>
  filter(Category != "Non-erotic", !ID %in% men) |>
  group_by(Category) |>
  slice_max(Homo_Women_Arousal, n=8, with_ties = FALSE) |>
  pull(ID) |> 
  c(
    napsero2 |>
      filter(Category != "Non-erotic", !ID %in% men) |>
      group_by(Category) |>
      slice_min(Homo_Women_Arousal, n=2, with_ties = FALSE) |>
      pull(ID)
  )

neutral <-  napsero2|>
  filter(Category == "Non-erotic", !ID %in% c(men, women)) |>
  mutate(Arousal = (Hetero_Men_Arousal + Hetero_Women_Arousal + Homo_Men_Arousal + Homo_Women_Arousal ) / 4) |>
  slice_min(Arousal, n=10, with_ties = FALSE) |>
  pull(ID)

pos_arousing <-  napsero2 |>
  filter(Category == "Non-erotic", !ID %in% c(men, women, neutral)) |>
  mutate(Arousal = (Hetero_Men_Arousal + Hetero_Women_Arousal + Homo_Men_Arousal + Homo_Women_Arousal) / 4,
         Valence = (Hetero_Men_Valence + Hetero_Women_Valence + Homo_Men_Valence + Homo_Women_Valence) / 4) |>
  filter(Valence > 5) |>
  slice_max(Arousal, n=10, with_ties = FALSE) |>
  pull(ID)

selected2 <- unique(c(men, homo_men, women, homo_women, neutral, pos_arousing))
selected_erotic_2 <- unique(c(men, homo_men, women, homo_women))

cat(
  paste0("N (men) = ", length(men), "\nN (homo_men) = ", length(homo_men),  "\nN (women) = ", length(women), "N (homo_women) = ", length(homo_women), "\nN (neutral) = ", length(neutral),  "\nN (arousing-positive) = ", length(pos_arousing),
       "\nTotal = ", length(selected2))
)
```

@@

dat2 |>
  filter(Category != "Non-erotic") |>
  ggplot(aes(x=Valence, y=Arousal)) +
  geom_point(aes(shape=Selected, color=Category), size=6, alpha=0.8) +
  ggside::geom_ysidedensity(data=filter(dat2, Selected), aes(color=Category), key_glyph = draw_key_blank) +
  ggside::geom_xsidedensity(data=filter(dat2, Selected), aes(color=Category), key_glyph = draw_key_blank) +
  # ggrepel::geom_label_repel(aes(label = label)) +
  scale_shape_manual(values=c("TRUE"=20, "FALSE"=4)) +
  scale_color_manual(values = c(
    "Opposite-sex Couple"="#673AB7", "Male Couple"= "#3F51B5", "Female Couple" = "#9C27B0",
    "Female" = "#E91E63", "Male"= "#2196F3")) +
  guides(shape = guide_legend(override.aes = list(color="white"))) +
  facet_grid(~Sexual_Orientation*Target) +
  theme_abyss() +
  theme(ggside.panel.grid.major = element_blank(), 
        ggside.axis.text = element_blank(),
        ggside.axis.line = element_blank())

@@

write.csv(selection_erotic2, "stimuli_data_erotic2.csv", row.names=FALSE)
knitr::kable(selection_erotic2)
```

>>>>

### Select based on norms
```{r}
men <- napsero2 |>
  filter(!Category %in% c("Non-erotic", "Male Couple", "Female Couple", "Male")) |>
  group_by(Category) |>
  slice_max(Hetero_Men_Arousal, n=8, with_ties = FALSE) |>
  pull(ID)

homo_men <- napsero2 |>
  filter(!Category %in% c("Non-erotic", "Female Couple", "Female", "Opposite-sex Couple")) |>
  group_by(Category) |>
  slice_max(Homo_Men_Arousal, n=8, with_ties = FALSE) |>
  pull(ID)

women <- napsero2 |>
  filter(!Category %in% c("Non-erotic", "Female Couple", "Male Couple", "Female"), !ID %in% men) |>
  group_by(Category) |>
  slice_max(Hetero_Women_Arousal, n=8, with_ties = FALSE) |>
  pull(ID)

homo_women <- napsero2 |>
  filter(!Category %in% c("Non-erotic", "Male Couple", "Male", "Opposite-sex Couple"), !ID %in% men) |>
  group_by(Category) |>
  slice_max(Homo_Women_Arousal, n=8, with_ties = FALSE) |>
  pull(ID) 
# 
# neutral <-  napsero2|>
#   filter(Category == "Non-erotic", !ID %in% c(men, women)) |>
#   mutate(Arousal = (Hetero_Men_Arousal + Hetero_Women_Arousal + Homo_Men_Arousal + Homo_Women_Arousal ) / 4) |>
#   slice_min(Arousal, n=10, with_ties = FALSE) |>
#   pull(ID)
# 
# pos_arousing <-  napsero2 |>
#   filter(Category == "Non-erotic", !ID %in% c(men, women, neutral)) |>
#   mutate(Arousal = (Hetero_Men_Arousal + Hetero_Women_Arousal + Homo_Men_Arousal + Homo_Women_Arousal) / 4,
#          Valence = (Hetero_Men_Valence + Hetero_Women_Valence + Homo_Men_Valence + Homo_Women_Valence) / 4) |>
#   filter(Valence > 5) |>
#   slice_max(Arousal, n=10, with_ties = FALSE) |>
#   pull(ID)

# selected2 <- unique(c(men, homo_men, women, homo_women, neutral, pos_arousing))

#only has unique images 
selected_erotic_2 <- c(men, women, homo_men,homo_women)

cat(
  paste0("N (men) = ", length(men), "\nN (homo_men) = ", length(homo_men),  "\nN (women) = ", length(women), "\nN (homo_women) = ", length(homo_women),
       "\nTotal = ", length(selected_erotic_2))
)

@@

# dat2 |>
#   filter(Category != "Non-erotic") |>
#   ggplot(aes(x=Valence, y=Arousal)) +
#   geom_point(aes(shape=Selected, color=Category), size=6, alpha=0.8) +
#   ggside::geom_ysidedensity(data=filter(dat2, Selected), aes(color=Category), key_glyph = draw_key_blank) +
#   ggside::geom_xsidedensity(data=filter(dat2, Selected), aes(color=Category), key_glyph = draw_key_blank) +
#   # ggrepel::geom_label_repel(aes(label = label)) +
#   scale_shape_manual(values=c("TRUE"=20, "FALSE"=4)) +
#   scale_color_manual(values = c(
#     "Opposite-sex Couple"="#673AB7", "Male Couple"= "#3F51B5", "Female Couple" = "#9C27B0",
#     "Female" = "#E91E63", "Male"= "#2196F3")) +
#   guides(shape = guide_legend(override.aes = list(color="white"))) +
#   facet_grid(~Sexual_Orientation*Target) +
#   theme_abyss() +
#   theme(ggside.panel.grid.major = element_blank(), 
#         ggside.axis.text = element_blank(),
#         ggside.axis.line = element_blank())

dat2 |>
  filter(Category != "Non-erotic") |>
  ggplot(aes(x = Valence, y = Arousal)) +
  geom_point(data = filter(dat2, Selected == FALSE),
             aes(shape = Selected, color = Category), size = 4, alpha = 0.3) +
  geom_point(data = filter(dat2, Sexual_Orientation == "Hetero", Target == "Men",
                           Category %in% c("Opposite-sex Couple", "Female"), 
                           ID %in% men | Selected == FALSE),
             aes(shape = Selected, color = Category), size = 6, alpha = 0.8) +
  geom_point(data = filter(dat2, Sexual_Orientation == "Hetero", Target == "Women",
                           Category %in% c("Opposite-sex Couple", "Male"),
                           ID %in% women | Selected == FALSE),
             aes(shape = Selected, color = Category), size = 6, alpha = 0.8) +
  geom_point(data = filter(dat2, Sexual_Orientation == "Homo", Target == "Men",
                           Category %in% c("Male Couple", "Male"), 
                           ID %in% homo_men | Selected == FALSE),
             aes(shape = Selected, color = Category), size = 6, alpha = 0.8) +
  geom_point(data = filter(dat2, Sexual_Orientation == "Homo", Target == "Women", 
                           Category %in% c("Female Couple", "Female"), 
                           ID %in% homo_women | Selected == FALSE),
             aes(shape = Selected, color = Category), size = 6, alpha = 0.8) +
  ggside::geom_ysidedensity(data = filter(dat2, Sexual_Orientation == "Hetero", Target == "Men",
                           Category %in% c("Opposite-sex Couple", "Female")),
                            aes(color = Category), key_glyph = draw_key_blank, alpha = 0.6) +
  ggside::geom_xsidedensity(data = filter(dat2, Sexual_Orientation == "Hetero", Target == "Men",
                           Category %in% c("Opposite-sex Couple", "Female")),
                            aes(color = Category), key_glyph = draw_key_blank, alpha = 0.6) +
  ggside::geom_ysidedensity(data = filter(dat2, Selected, Sexual_Orientation == "Hetero", Target == "Women", 
                           Category %in% c("Opposite-sex Couple", "Male")),
                            aes(color = Category), key_glyph = draw_key_blank, alpha = 0.6) +
  ggside::geom_xsidedensity(data = filter(dat2, Selected, Sexual_Orientation == "Hetero", Target == "Women", 
                           Category %in% c("Opposite-sex Couple", "Male")),
                            aes(color = Category), key_glyph = draw_key_blank, alpha = 0.6) +
  ggside::geom_ysidedensity(data = filter(dat2, Sexual_Orientation == "Homo", Target == "Men",
                           Category %in% c("Male Couple", "Male")),
                            aes(color = Category), key_glyph = draw_key_blank, alpha = 0.6) +
  ggside::geom_xsidedensity(data = filter(dat2, Sexual_Orientation == "Homo", Target == "Men",
                           Category %in% c("Male Couple", "Male")),
                            aes(color = Category), key_glyph = draw_key_blank, alpha = 0.6) +
  ggside::geom_ysidedensity(data = filter(dat2, Selected, Sexual_Orientation == "Homo", Target == "Women", 
                           Category %in% c("Female Couple", "Female")),
                            aes(color = Category), key_glyph = draw_key_blank, alpha = 0.6) +
  ggside::geom_xsidedensity(data = filter(dat2, Selected, Sexual_Orientation == "Homo", Target == "Women", 
                           Category %in% c("Female Couple", "Female")),
                            aes(color = Category), key_glyph = draw_key_blank, alpha = 0.6) +
  scale_shape_manual(values = c("TRUE" = 20, "FALSE" = 4)) +
  scale_color_manual(values = c(
    "Opposite-sex Couple" = "#673AB7", "Male Couple" = "#3F51B5", "Female Couple" = "#9C27B0",
    "Female" = "#E91E63", "Male" = "#2196F3")) +
  guides(shape = guide_legend(override.aes = list(color = "white"))) +
  facet_grid(~Sexual_Orientation * Target) +
  theme_abyss() +
  theme(ggside.panel.grid.major = element_blank(), 
        ggside.axis.text = element_blank(),
        ggside.axis.line = element_blank())

@@

write.csv(selection_erotic2, "stimuli_data2.csv", row.names=FALSE)
knitr::kable(selection_erotic2)
```
